### 2018-10-03 README.Rmd
fix figure link
link to figures and tables

## Vision

Use more detailed Ag and soils data to improve predictive models of lake TP, TN, and Nitrate.

@@

```{r maps, echo=FALSE}
knitr::include_graphics("../../fig/rmd-hi_ag_iws_w_ep-1.png")
```

@@

```{r lagos_v_cdl_v_usgs, echo=FALSE}
# tp vs lagos ag, cdl ag, usgs P inputs

>>>>

Code and data for:

## The effect of crop type, fertilizer, and manure applications on lake nutrients in agriculture watersheds at regional scales

> Journal Target: Ecosystems

### Products

Figures: [manuscript/figures.pdf](manuscript/figures.pdf)

Tables: [manuscript/tables.pdf](manuscript/tables.pdf)

@@

```{r maps, echo=FALSE}
knitr::include_graphics("figures/rmd-hi_ag_iws_w_ep-1.png")
```

@@

```{r lagos_v_cdl_v_usgs, echo=FALSE, eval=FALSE}
# tp vs lagos ag, cdl ag, usgs P inputs
